\documentclass[a4paper, 12pt, openright, oneside, final]{book}%{scrbook}
\usepackage{eso-pic}
\usepackage{float}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage[english]{babel}
\usepackage{listings}
\usepackage{varioref}
\usepackage{subfigure}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage[pdftex,bookmarks=true,hypertexnames=true]{hyperref}
\usepackage{fancyhdr}
\newcommand{\fncyblank}{\fancyhf{}}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\usepackage{lettrine}
\newenvironment{abstract}%
{\cleardoublepage\fncyblank\null\vfill\begin{center}%
\bfseries\abstractname\end{center}}%
{\vfill\null}

%\lstset{%
%  basicstyle=\small,
%  frame=tb,
%  captionpos=b,
%  stringstyle=\ttfamily,
%  showstringspaces=false,
%  numbers=left,
%  numberstyle=\tiny,
%  framextopmargin=2pt,
%  framexbottommargin=2pt,
%  stepnumber=1,
%  numbersep=5pt}

\usepackage{courier}
\usepackage{color}
\usepackage{xcolor}
\lstset{
         basicstyle=\footnotesize\ttfamily, % Standardschrift
         %numbers=left,               % Ort der Zeilennummern
         numberstyle=\tiny,          % Stil der Zeilennummern
         %stepnumber=2,               % Abstand zwischen den Zeilennummern
         numbersep=5pt,              % Abstand der Nummern zum Text
         tabsize=2,                  % Groesse von Tabs
         extendedchars=true,         %
         breaklines=true,            % Zeilen werden Umgebrochen
         keywordstyle=\color{red},
 %        frame=b,         
 %        keywordstyle=[1]\textbf,    % Stil der Keywords
 %        keywordstyle=[2]\textbf,    %
 %        keywordstyle=[3]\textbf,    %
 %        keywordstyle=[4]\textbf,   \sqrt{\sqrt{}} %
         stringstyle=\color{black}\ttfamily, % Farbe der String
         showspaces=false,           % Leerzeichen anzeigen ?
         showtabs=false,             % Tabs anzeigen ?
         xleftmargin=5pt,
         framexleftmargin=5pt,
         framexrightmargin=5pt,
         framexbottommargin=4pt,
         %backgroundcolor=\color{lightgray},
         showstringspaces=false      % Leerzeichen in Strings anzeigen ?        
}
\lstloadlanguages{% Check Dokumentation for further languages ...
         %[Visual]Basic
         %Pascal
         C
         %C++
         %XML
         %HTML
         %Java
}
%\DeclareCaptionFont{blue}{\color{blue}} 

\usepackage{caption} \DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox[cmyk]{0.43, 0.35,
0.35,0.01}{\parbox{\textwidth}{\hspace{15pt}#1#2#3}}}
\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white,
singlelinecheck=false, margin=0pt, font={bf,footnotesize}}

\hypersetup{
pdfauthor= {Sun Youcheng},
pdftitle= {Design and Development of Real-Time Multi-Processor Bandwidth
Control Mechanisms in General Purpose Operating Systems},
pdfsubject= {Design and Development of Real-Time Multi-Processor Bandwidth
Control Mechanisms in General Purpose Operating Systems},
pdfkeywords = {realtime, scheduling, linux, multiprocessor, hierarchy},
pdfborder = { 0 0 0 0 }
}

%
% TODO: it is better to use title and author keywords here
%
\title{Design and Development of Real-Time Multi-Processor Bandwidth
  Control Mechanisms in General Purpose Operating Systems}

\author{Youcheng Sun}

\onehalfspacing

\begin{document}

\frontmatter

%\maketitle

\input{frontpage}
\input{dedication}
\begin{abstract}
  % TODO: the abstract should be a short summary of the contents of
  % the thesis. Very short motivation (the problem to be solved), and
  % what has been done in the thesis.
  % DONE

  %Attentions have been being paid to extend general purpose operating
  %systems with real time functionalities. In this thesis, a scheduling
  %framework, which can control Central Processing Unit (CPU) bandwidth
  %distribution on multi-processor platforms in a real-time way, is
  %proposed in Linux.  Under the framework, cpu bandwidths from
  %different processors are reserved according to Constant Bandwidth
  %Server (CBS) rules.  Yet as for how to utilize the reserved
  %bandwidths to schedule tasks in Linux, this is not the interest of
  %the framework. They can be scheduled by policies used in the Linux
  %system or scheduling algorithms that are implemented for a specific
  %purpose. A subset of these tasks can get a portion of the
  %reservation using the same rule.  Furthermore, under the framework,
  %scheduling policies can be applied in a controlled scale instead of
  %the whole system.

  %In current implementation, both normal tasks and real-time tasks in
  %Linux can work under the framework. Experimental results are not
  %available now ...
  Attentions have been being paid to extend general purpose operating
  systems (GPOS) with real time functionalities. In this thesis, the
  Open-Extension Container(OXC) scheduling framework, which can control 
  Central Processing Unit (CPU) bandwidth distribution on multi-processor 
  platforms in a real-time way, is proposed in Linux. The ox container 
  is a new data structure defined in our work. It has a good feature 
  that from a Linux scheduler's aspect, it behaves as a virtual CPU.  
  Under the framework, CPU bandwidths from different processors are 
  reserved according to Constant Bandwidth Server (CBS) rules.  Yet 
  as for how to utilize the reserved bandwidths to schedule tasks, 
  this is not the interest of the framework. They can be scheduled by 
  policies used in the Linux system or scheduling algorithms that are 
  implemented for a specific purpose. A subset of these tasks can get 
  a portion of the reservation using the same rule.  Furthermore, under 
  the framework, scheduling policies can be applied in a controlled scale 
  instead of the whole system.

  In current implementation, both normal tasks and real-time tasks in
  Linux can work under the framework. Experiments show that our 
  hierarchical CPU bandwidth control is feasible in Linux.
\end{abstract}

\tableofcontents
\listoffigures
\lstlistoflistings
\input{introduction}
\mainmatter
\input{background}
\input{design}
\input{impl}
\input{exp}
\input{conclusion}
\backmatter
\input{acknowledgements}

\bibliographystyle{ieeetr}%{plain}
\bibliography{biblio}

\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
